Niche complementarity among pollinators increases community-level plant reproductive success

### 2020-04-30 Network_structure_and_function.Rmd
small error in discussion

The existence of relationships between interaction network structure and ecosystem function have been long hypothesized, yet, the specific mechanisms underlying this relationship remain elusive [@Thompson2012]. Our results suggest that different aspects of network structure affect different dimensions of ecosystem functioning. Specifically, we find that the centrality of a plant species within a community has a positive association with its fruit set, indicating that from a plant's perspective, being connected to other plant species via shared pollinators has a positive outcome (e.g. by ensuring a stable pollinator supply through time) rather than a negative one (e.g. via heterospecific pollen transport). At the site level, we find that greater values of niche complementarity between pollinators result in larger average values of reproductive success.

>>>>

The existence of relationships between interaction network structure and ecosystem function have been long hypothesized, yet, the specific mechanisms underlying this relationship remain elusive [@Thompson2012]. Our results suggest that different aspects of network structure affect different dimensions of ecosystem functioning. Specifically, we find that the contribution to nestedness of a plant species within a community has a positive association with its fruit set. From a plant's perspective, this indicates that being connected to other plant species via shared pollinators has a positive outcome (e.g. by ensuring a stable pollinator supply through time) rather than a negative one (e.g. via heterospecific pollen transport). At the site level, we find that greater values of niche complementarity between pollinators result in larger average values of reproductive success.
